Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation

### 2014-03-05 writedown/npt-neq/submit.tex
convert for submission

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\includegraphics[height=3.6cm]{fig.ala.new/graphs/final-3.eps}
% Some journals require a graphical entry for the Table of Contents.
% This should be laid out ``print ready'' so that the sizing of the
% text is correct.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig.ala.new/fig.all/fig-all.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): Two dihedral angles
    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
    (b): The equilibrium probability density 
    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
    indicates higher probability.
    Plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $\confaa = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $\confab = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $\confba = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $\confbb = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $\confc   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
    Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
    on the plot (b) and (c).
    % Considering the angular periodicity, if we write, for example,
    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
    This division is the same for both plot (b) and (c).
  }
  \label{fig:tmp4}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala.new/fig-meta-more.eps}
  \caption{The time-dependent probability of conformations $P_I(t)$ 
    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = \confaa$,
    green to $\confab$, dark blue to $\confba$, purple to $\confbb$ and light blue
    to $\confc$. {
      The solid lines denote the results of one branching trajectory
      starting from each initial conformation, while the dashed lines denote
      the average of the four branching trajectories (different random seeds for the Langevin thermostat, see text) starting from each initial
      conformation.
      The shadowed region with each solid line denotes the
      statistical uncertainty of the result at 95\% confidence level.
    }
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-5.eps}
  \caption{
    The net probability flux for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
    From top, left to right we report $I = \confaa$, $\confab$, $\confba$; bottom, left to right $\confbb$ and
    $\confc$, respectively. In each plot, the red line stands for $J=\confaa$,
    green for $J=\confab$, dark blue for $J=\confba$, purple for $J=\confbb$ and light blue
    for $J=\confc$.
    {This plot is drawn from the four-branching-trajectories case (see the text).}
    }
  \label{fig:tmp6}
\end{figure}
The time-dependent probability density of the system to stay in a certain
conformation is given in
Fig.~\ref{fig:tmp5}.
In order to show that  our simulation results are robust with respect to the randomness introduced by the (local) Langevin thermostat, we have tested the effects of changing random seeds for the thermostat in the thermostated region. We compared simulation results obtained by starting a branching trajectory
from each initial conformation with those obtained from four different branching trajectories from each initial conformation (each of four with
different random seed for the Langevin thermostat in the thermostated region).
Results are consistent within the statistical uncertainty (see Fig.\ref{fig:tmp5}).
The $\beta$-sheet conformations $\confba$ and $\confbb$,
which are present at the initial stage after EF is switched on,
{fade away as the system relaxes}. The
probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes {of the four-branching-trajectories case} in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero,
however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system is driven away from the initial
equilibrium (at zero EF),  starting a dynamical nonequilibrium process.
After sufficiently long time, the system
is fully relaxed to the new stationary state, in
which it remains as long as the EF is switched on.
Of course we cannot exclude very slow nonequilibrium processes,
which cannot be captured by the duration of
our nonequilibrium simulation (1~ns), since it is
obviously that the proposed nonequilibrium approach
can only study time-dependent behaviours that are shorter than
the total time of the branching trajectories. 
% After a time long enough, the system
% is fully relaxed to the new equilibrium defined by the action of the constant EF,
% and stays there as long as the EF is kept.
An important point is that despite the system is finally relaxed to the new conformation,
the relaxation timescales corresponding to each conformation are rather different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.

@@

\subsection{Molecular dipole response}
The fact that our external perturbation corresponds to the action of
an electric field, naturally leads to the question 
  of the alignment of the molecular dipole vector along the direction of external EF, and, in turn, of how this is related
to the overall conformational change of the molecule as reported in
the previous section.
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig.ala.new/field.dipole/fig-dipol-order-conf.eps}
  \caption{The
    $x$-component of the molecular dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The solid line represents the dipole moment,
    while the dashed line represents the orientational order parameter.
    The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala.new/fig-meta-conv.eps}
  \caption{Testing the finite-size effect on the dynamical and thermostated region.
    Probabilities of different conformations are presented versus time.
    See the text for more details.
    {The shadowed region denotes the
      statistical uncertainty of the $L=2.7$~nm $R_{ex}=1.0$~nm case at 95\% confidence level.
    }
  }
  \label{fig:tmp7}
\end{figure}

@@

\section{Case II:
  periodically oscillatory EF}
A step forward in our study is to consider a periodically oscillatory EF which has
a $\sin$-wave shape:
\begin{align}
  \vect E(t) = (E_0\sin(2\pi t / \period), 0, 0),
\end{align}
where $E_0$ is the intensity of the field, which is chosen to be
1.0~V/nm.  $\period$ is the oscillating period.
Here we tested three different
periods 10, 40 and 200~ps.
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-order.eps}
  \caption{Illustration of the effect of the oscillatory EF on the system:
    (a) the dipole moment  and (b) the
    orientational order parameter of alanine dipeptide as a
    function of time. In (a),
    only the $x$-component of the dipole moment is
    shown. The black line refers to the static EF which is turned on
    at time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
    10~ps. The green line is of 40~ps; and the blue of 200~ps.}
  \label{fig:tmp8}
\end{figure}
Fig.~\ref{fig:tmp8} (a)
presents the $x$-component of the molecular dipole moment as
a function of time. The red, green and blue lines report the
results of $\period =10$~ps, 40~ps and 200~ps, respectively. The black line
shows the dipole moment under constant EF
for reference.
It shows that the oscillating period of the molecular dipole moment
is the same as the period of the oscillatory EF. Therefore,
the molecular dipole moment
is able to respond to the external EF almost immediately.
At $\period =200$~ps, the maximum magnitude of the molecular
dipole moment is close to the value obtained in the case of constant EF, which
means that the variation of the oscillatory EF is so slow that the
alanine has enough time to 
relax its dipole. However,
for $\period =10$ and 40~ps, the EF oscillates faster and the molecule 
does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
Fig.~\ref{fig:tmp8}~(b) presents the orientational order
parameter. The notations are the same as Fig~\ref{fig:tmp8}~(a).
For all cases the order parameter is much
smaller than in the case of constant EF. One possible reason is that the
relaxation of the order parameter is very slow, and the molecule in the case of oscillatory field is
not exposed to a strong enough EF for a time long enough.
For  $\period =10$ and 40~ps, the orientation of the alanine shows a {very} weak tendency
to be parallel to the EF. It is worth to notice that for constant EF,
we also observe a quick alignment of the molecular orientation vector to the EF
on the time scale of 10~ps. For $\period =200$~ps, the molecule tends periodically
to be more perpendicular to the EF, but this directional preference is much
weaker than in the case of constant EF.

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
  \caption{The probability of being in a given of conformation for alanine in a   periodically oscillatory EF. Different periods,
    i.e. $\period =10$~ps, 40~ps and 200~ps, are considered here.  The
    probability of being in a certain conformation $I$, which is
    denoted by $P_I$ in this paper, is plotted by colored lines against
    time. Red line: $I = \confaa$,  green line: $I = \confab$,  dark
    blue line: $I = \confba$,  pink line: $I = \confbb$ and  light blue
    line: $I = \confc$. For $\period =10$~ps and 40~ps, the nonequilibrium
    simulations last 1000~ps, while for $\period =200$~ps,
    they last 6400~ps.  }
  \label{fig:tmp9}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-5.eps}\\
  \caption{
    Integrated probability flux $Q_{J,I}(t)$ for the periodically
    oscillatory EF, is plotted against time (horizontal axis, in picoseconds).
    The integrated
    probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
    $F_{J,I}(t)$ is the net probability flux from conformation $J$ to $I$.
    See also Eqn.~\eqref{eqn:tmp7} and~\eqref{eqn:tmp7a} for definitions
    of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.
    From top to bottom, rows report results with  period 10, 40 and 200~ps, respectively.
    From left to right, the five
    columns show the integrated flux $Q_{J,\confaa}$, $Q_{J,\confab}$,
    $Q_{J,\confba}$, $Q_{J,\confbb}$ and $Q_{J,\confc}$, respectively. In each plot,
    the red line stands for $J=\confaa$, green for $J=\confab$, dark blue for $J=\confba$,
    purple for $J=\confbb$ and light blue for $J=\confc$.
    An increasing value of $Q_{J,I}$ indicates a net probability
      flux from conformation $J$ to $I$,
      while a decreasing value of $Q_{J,I}$ indicates a net probability
      flux from $I$ to $J$.
  }
  \label{fig:tmp10}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\includegraphics[height=3.6cm]{final-3.eps}
% Some journals require a graphical entry for the Table of Contents.
% This should be laid out ``print ready'' so that the sizing of the
% text is correct.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig-all.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): Two dihedral angles
    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
    (b): The equilibrium probability density 
    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
    indicates higher probability.
    Plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $\confaa = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $\confab = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
    $\confba = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $\confbb = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
    $\confc   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
    Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
    on the plot (b) and (c).
    % Considering the angular periodicity, if we write, for example,
    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
    This division is the same for both plot (b) and (c).
  }
  \label{fig:tmp4}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-more.eps}
  \caption{The time-dependent probability of conformations $P_I(t)$ 
    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = \confaa$,
    green to $\confab$, dark blue to $\confba$, purple to $\confbb$ and light blue
    to $\confc$. {
      The solid lines denote the results of one branching trajectory
      starting from each initial conformation, while the dashed lines denote
      the average of the four branching trajectories (different random seeds for the Langevin thermostat, see text) starting from each initial
      conformation.
      The shadowed region with each solid line denotes the
      statistical uncertainty of the result at 95\% confidence level.
    }
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-1.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-2.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-3.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-4.eps}
  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
  \caption{
    The net probability flux for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
    From top, left to right we report $I = \confaa$, $\confab$, $\confba$; bottom, left to right $\confbb$ and
    $\confc$, respectively. In each plot, the red line stands for $J=\confaa$,
    green for $J=\confab$, dark blue for $J=\confba$, purple for $J=\confbb$ and light blue
    for $J=\confc$.
    {This plot is drawn from the four-branching-trajectories case (see the text).}
    }
  \label{fig:tmp6}
\end{figure}
The time-dependent probability density of the system to stay in a certain
conformation is given in
Fig.~\ref{fig:tmp5}.
In order to show that  our simulation results are robust with respect to the randomness introduced by the (local) Langevin thermostat, we have tested the effects of changing random seeds for the thermostat in the thermostated region. We compared simulation results obtained by starting a branching trajectory
from each initial conformation with those obtained from four different branching trajectories from each initial conformation (each of four with
different random seed for the Langevin thermostat in the thermostated region).
Results are consistent within the statistical uncertainty (see Fig.\ref{fig:tmp5}).
The $\beta$-sheet conformations $\confba$ and $\confbb$,
which are present at the initial stage after EF is switched on,
{fade away as the system relaxes}. The
probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes {of the four-branching-trajectories case} in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero,
however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system is driven away from the initial
equilibrium (at zero EF),  starting a dynamical nonequilibrium process.
After sufficiently long time, the system
is fully relaxed to the new stationary state, in
which it remains as long as the EF is switched on.
Of course we cannot exclude very slow nonequilibrium processes,
which cannot be captured by the duration of
our nonequilibrium simulation (1~ns), since it is
obviously that the proposed nonequilibrium approach
can only study time-dependent behaviours that are shorter than
the total time of the branching trajectories. 
% After a time long enough, the system
% is fully relaxed to the new equilibrium defined by the action of the constant EF,
% and stays there as long as the EF is kept.
An important point is that despite the system is finally relaxed to the new conformation,
the relaxation timescales corresponding to each conformation are rather different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.

@@

\subsection{Molecular dipole response}
The fact that our external perturbation corresponds to the action of
an electric field, naturally leads to the question 
  of the alignment of the molecular dipole vector along the direction of external EF, and, in turn, of how this is related
to the overall conformational change of the molecule as reported in
the previous section.
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
  \caption{The
    $x$-component of the molecular dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The solid line represents the dipole moment,
    while the dashed line represents the orientational order parameter.
    The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-conv.eps}
  \caption{Testing the finite-size effect on the dynamical and thermostated region.
    Probabilities of different conformations are presented versus time.
    See the text for more details.
    {The shadowed region denotes the
      statistical uncertainty of the $L=2.7$~nm $R_{ex}=1.0$~nm case at 95\% confidence level.
    }
  }
  \label{fig:tmp7}
\end{figure}

@@

\section{Case II:
  periodically oscillatory EF}
A step forward in our study is to consider a periodically oscillatory EF which has
a $\sin$-wave shape:
\begin{align}
  \vect E(t) = (E_0\sin(2\pi t / \period), 0, 0),
\end{align}
where $E_0$ is the intensity of the field, which is chosen to be
1.0~V/nm.  $\period$ is the oscillating period.
Here we tested three different
periods 10, 40 and 200~ps.
\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
  \caption{Illustration of the effect of the oscillatory EF on the system:
    (a) the dipole moment  and (b) the
    orientational order parameter of alanine dipeptide as a
    function of time. In (a),
    only the $x$-component of the dipole moment is
    shown. The black line refers to the static EF which is turned on
    at time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
    10~ps. The green line is of 40~ps; and the blue of 200~ps.}
  \label{fig:tmp8}
\end{figure}
Fig.~\ref{fig:tmp8} (a)
presents the $x$-component of the molecular dipole moment as
a function of time. The red, green and blue lines report the
results of $\period =10$~ps, 40~ps and 200~ps, respectively. The black line
shows the dipole moment under constant EF
for reference.
It shows that the oscillating period of the molecular dipole moment
is the same as the period of the oscillatory EF. Therefore,
the molecular dipole moment
is able to respond to the external EF almost immediately.
At $\period =200$~ps, the maximum magnitude of the molecular
dipole moment is close to the value obtained in the case of constant EF, which
means that the variation of the oscillatory EF is so slow that the
alanine has enough time to 
relax its dipole. However,
for $\period =10$ and 40~ps, the EF oscillates faster and the molecule 
does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
Fig.~\ref{fig:tmp8}~(b) presents the orientational order
parameter. The notations are the same as Fig~\ref{fig:tmp8}~(a).
For all cases the order parameter is much
smaller than in the case of constant EF. One possible reason is that the
relaxation of the order parameter is very slow, and the molecule in the case of oscillatory field is
not exposed to a strong enough EF for a time long enough.
For  $\period =10$ and 40~ps, the orientation of the alanine shows a {very} weak tendency
to be parallel to the EF. It is worth to notice that for constant EF,
we also observe a quick alignment of the molecular orientation vector to the EF
on the time scale of 10~ps. For $\period =200$~ps, the molecule tends periodically
to be more perpendicular to the EF, but this directional preference is much
weaker than in the case of constant EF.

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
  \caption{The probability of being in a given of conformation for alanine in a   periodically oscillatory EF. Different periods,
    i.e. $\period =10$~ps, 40~ps and 200~ps, are considered here.  The
    probability of being in a certain conformation $I$, which is
    denoted by $P_I$ in this paper, is plotted by colored lines against
    time. Red line: $I = \confaa$,  green line: $I = \confab$,  dark
    blue line: $I = \confba$,  pink line: $I = \confbb$ and  light blue
    line: $I = \confc$. For $\period =10$~ps and 40~ps, the nonequilibrium
    simulations last 1000~ps, while for $\period =200$~ps,
    they last 6400~ps.  }
  \label{fig:tmp9}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\
  \caption{
    Integrated probability flux $Q_{J,I}(t)$ for the periodically
    oscillatory EF, is plotted against time (horizontal axis, in picoseconds).
    The integrated
    probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
    $F_{J,I}(t)$ is the net probability flux from conformation $J$ to $I$.
    See also Eqn.~\eqref{eqn:tmp7} and~\eqref{eqn:tmp7a} for definitions
    of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.
    From top to bottom, rows report results with  period 10, 40 and 200~ps, respectively.
    From left to right, the five
    columns show the integrated flux $Q_{J,\confaa}$, $Q_{J,\confab}$,
    $Q_{J,\confba}$, $Q_{J,\confbb}$ and $Q_{J,\confc}$, respectively. In each plot,
    the red line stands for $J=\confaa$, green for $J=\confab$, dark blue for $J=\confba$,
    purple for $J=\confbb$ and light blue for $J=\confc$.
    An increasing value of $Q_{J,I}$ indicates a net probability
      flux from conformation $J$ to $I$,
      while a decreasing value of $Q_{J,I}$ indicates a net probability
      flux from $I$ to $J$.
  }
  \label{fig:tmp10}
\end{figure}

Fig.~\ref{fig:tmp9} shows the probability of the
conformations against time for periodically oscillatory EF,
while  
Fig.~\ref{fig:tmp10} presents the integrated net probability fluxes
(defined by Eqn.~\eqref{eqn:tmp7a}) between
conformations. Here the probability fluxes are not reported
because the profiles are highly oscillating and they would not offer 
a better information than the one that can be obtained from the integrated probability flux.
Coming back to Fig.~\ref{fig:tmp9}, for all periods investigated,
the observed time-dependent probabilities  in $\confaa$, $\confab$, $\confba$ and $\confbb$ are
highly oscillating and the average value over time cycles does not change
considerably w.r.t.~time.
However, the probability in conformation $\confc$ significantly
increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
0.26 for $\period =200$~ps.
In the case of $\period =10$ and $40$~ps, {the probability of conformation $\confc$}
reaches the steady value in around 300~ps, while it requires about 1200~ps
for the $\period =200$~ps case. 
The notable increment of probability of $\confaa$ and
  the vanishing of $\confba$ in the constant EF case (see Fig.~\ref{fig:tmp5})
are not observed in the oscillatory EF case.
\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{graph-t0010-2.eps}
  \caption{Schematic plot of the main probability fluxes between conformations
    for oscillatory EF, $\period =10$~ps. The thickness 
    of the arrows approximately presents the strength of the flux.
    The numbers near the arrows indicates the strength of the averaged
    probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
  }
  \label{fig:tmp11}
\end{figure}
In comparison to the static EF case, where the probability flux
vanishes when the system reaches steady state (Fig.~\ref{fig:tmp6}), 
Fig.~\ref{fig:tmp10} shows increasing
integrated probability net fluxes, which imply some lasting and directional
fluxes among the conformations {in steady state}.
Fig.~\ref{fig:tmp11} presents
a schematic plot of the main probability fluxes for $\period =10$~ps.
The thickness of the arrows and the numbers nearby indicate
the steady value of average net fluxes over periods.
The relevance of Fig.~\ref{fig:tmp11} is in the fact that it suggests,
in perspective, a general scenario common to all molecules
characterized by $\beta$-sheet-like or $\alpha$-helix-like
conformations and how an electric field is likely to modify it.
  Although the network presented in Fig.~\ref{fig:tmp11} is similar to those
  discovered in the equilibrium studies 
  in the sense of the steady conformations and connections among them (e.g.~in Ref.~\cite{apostolakis1999calculation, gfeller2007complex}),
  the physical meaning is quite different in our study:
  The system is under nonequilibrium conditions due to a controlled physical external perturbation, and
  the related net probability fluxes are based on trajectories generated by such a perturbation. In contrast, in the equilibrium studies,
  such net probability fluxes do not explicitly exist.
The probability flux of $\period =40$~ps is quantitatively
comparable to the case $\period =10$~ps, except that the probability fluxes
going into conformation $\confc$ is stronger, which actually results in
a higher steady probability in $\confc$.
The probability flux of case $\period =200$~ps is qualitatively
similar to $\period =10$~ps and $\period =40$~ps, however,
the strength is much lower than the latter two cases.
Moreover, 
  we see that the integrated fluxes reach
  a steadily
increasing stage after about 3200~ps, which is even longer than the time scale
at which the probability of $\confc$ reaches its steady value. This indicates
a longer intrinsic time scale in the $\period =200$~ps case.
